Tropical Andes plant trait data BIEN

### 2025-08-18 code/L0/L0_TropicalAndes_plants_BIEN_traits.Rmd
Added name; cannot run line 45 (error regarding vector size), but the tropical Andes subset of plant trait data (line 50) works

---
title: "Tropical Andes plant trait data BIEN"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script retrieves plant trait data from the BIEN database for Tropical Andean countries."
data input: "none"
data output: "TropicalAndes_BIEN_traits.csv, AllDesired_BIEN_plant_traits.csv"
date: "2023-10-17"
output: html_document
---

>>>>

---
title: "Tropical Andes plant trait data BIEN"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske, and Jenna B. Baljunas"
overview: "This script retrieves plant trait data from the BIEN database for Tropical Andean countries."
data input: "none"
data output: "TropicalAndes_BIEN_traits.csv, AllDesired_BIEN_plant_traits.csv"
date: "2023-10-17"
output: html_document
---
